{\bf Task~1.}~~{\it Read the following text. Translate the unslerlined words into Russian using the
vocabulary given in the end of the book.}\par
Within customer premises the importance of the cabling infrastracture is similar to that of other
fundamental building utilities such as heating, lighting and mains power. As with other utilities,
interruptions to service can have serious impact. Poor quality of service due to lack of design foresight,
use of inappropriate components, incorrect installation, poor administration or inadequate support can
threaten an organization's effectiveness.\par
Historically, the cabling within a premises comprised both application specific and multipurpose
networks. Appropriate use of the International Standard will enable a controlled migration to generic
cabling. Certain circumstances may warrant the introduction of application specific cabling; these
instances should be minimized.\par

{\bf Task~2.}~~{\it Read the text given in {\bf task 1} again and translate the following words and word
combinations into Russian.}\par
Fundamental, must impuct, interruptions to service, serious impact, poor quality, luck, design
foresight, inappropriate, components, controlled migration, circumstances, warrant, introduction, instances.\par

{\bf Task~3.}~~{\it Retell the text from {\bf task 1}.}\par

{\bf Task~4.}~~{\it Translate the following word combinations into Russian. Use the vocabulary given in the end
of the book}\par
Application independent generic cabling system; open market for cabling components; flexible
cabling scheme; building professionals; accomodution \textbf{FFF} of cabling; initial planning; refurbishment;
stundardisation bodies; current product; product development; multi-vendor cablingl ropper cabling;
premises geography; general pffice environment; life expectancy.\par

{\bf Task~5.}~~{\it Translate the following sentences into English.}\par
\begin{enumerate}
    \item {Структурированная кабельная система используется в коммерческих помещениях,
    расположенных в отдельных зданиях или группах зданий одного комплекса.}
    \item {Данная структурированная кабельная система предназначена для огромных помещений площадью 1000000 м$^2$.}
    \item {Кабельная система, определенная данным Международным стандартом, поддерживает
    широкий диапазон услуг, включая голосовые, видео, передачу изображения, текста и данных.}
    \item {Необходимо определить структуру и минимальную конфигурацию кабельной системы, а
    также требования к работе определенных кабельных соединений}
    \item {При установке и монтаже кабельной системы необходимо учесть требования 
    противопожарной безопасности}
    \item {В данном стандарте предлагается следующее определение кабельного элемента:
    кабельный элемент -- наименьшая составляющая кабеля; кабельный элемент может быть защищен.}
    \item {Конфигурация кабельной системы должна соответствовать требованиям, изложенным в
    разделе 5}
    \item {Вся кабельная система состоит из соединений, уровень которых соответствует стандарту}
    \item {Во многих сериях интерфейс сети общего пользователя является точкой соединения
    оборудования провайдера сети и кабельной системы помещений пользователя.}
\end{enumerate}

{\bf Task~6.}~~{\it ...}\par














